---
title: "Introduction to the ML Studio Package"
author: "Rami Krispin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The ML Studio package is a Shiny based platform for statistical modeling and machine learning applications. The package is under construction and currently is available for download throw github. 
 
## **Current features:**

1. Data Management:

* Ability to load data from multiple sources (csv file, R global environment, R datasets)

* Summary data with dplyr based function

* Control and modify variables attributes 

2. Interactive data visualization with based on the Plotly package:

* Scatter, line, histogram correlation, etc.

* Time series plots – seasonality, correlation etc.

3. Machine learning and deep learning algorithms with the H2O package, currently only classification models available (Deep Learning, Random Forest, GBM, GLM)

## **Under construction features:**

1. Additional regression and classification and deep learning models with caret, H2O and Keras

2. Time series analysis and forecasting models with the forecast package

3. Cluster analysis 

4. Parameters tuning with grid search

5. Ability to communicate model results

## Get start

Until the devtool version of the package will be ready, the package can be sourced from github. The key requirements prior for sourcing the package from github is the Shiny and H2O packages:

Installing shiny is straightforward using the code below:

```{r eval=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
install.packages("shiny")
```

The installation of H2O can be done with the following code:

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, eval=FALSE}
# The following two commands remove any previously installed H2O packages for R.
if ("package:h2o" %in% search()) { detach("package:h2o", unload=TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }

# Next, we download packages that H2O depends on.
pkgs <- c("statmod","RCurl","jsonlite")
for (pkg in pkgs) {
if (! (pkg %in% rownames(installed.packages()))) { install.packages(pkg) }
}

# Now we download, install and initialize the H2O package for R.
install.packages("h2o", type="source", repos="https://h2o-release.s3.amazonaws.com/h2o/rel-weierstrass/7/R")

# Finally, let's load H2O and start up an H2O cluster
library(h2o)
h2o.init()
```

Java add-ons may be required, additional information about download and installation option of H2O is available [here](https://h2o-release.s3.amazonaws.com/h2o/rel-weierstrass/7/index.html).





Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r fig.show='hold', message=FALSE, warning=FALSE, paged.print=FALSE}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
